Insert the article title here

### 2018-06-29 writeup/manuscript.tex
Some more edits

In the current study, we focus on one source of individual differences in visual search: strategy. By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation. Perhaps surprisingly, previous literature has shown that both ideal oberver \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise. These apparent contradictory results could potentially expained by large individual differences.

A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They carried out a dynamic dot detection task 
found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.

\end{fmtext}

Also \cite{proulx2011}

In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters. The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} examined strategies in the use of feature-based attention\cite{irons-leber2016,irons-leber2018} \ldots. Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to nearly optimal), and how often they changed search features. Even larger differences [haha we might argue with that, depending what you mean by larger] were found with the Split-Half Search Arrays \cite{nowakowsak2017} who aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies. They found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to match the performance of the stochastic searcher. Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.

\maketitle

Mention \cite{amor2017}

@@

[MAYBE THERE SHOULD BE SOMETHING ELSE TO SET UP THE RESEARCH Q?] A common theme emerging from the studies in the observation that individual strategies vary in their degree of effectiveness or optimality [IF THAT IS EVEN A WORD]. However, each task taps into a different aspect of visual search behavior (feature-based attention, [spatial/fixation patterns??]). The aim of the present study is to investigate the extent to which these differences are stable across different visual search paradigms. Are observers who use the optimal strategy in the split-half search arrays also more optimal in the ACVS task? Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms? As a secondary question, we will measure the test-retest reliability of the differences found in the split-half array paradigm.

@@

The multiple-target foraging results were also in line previous findings \cite{kristjansson2014,johannesson2016}. As expected, run lengths were shorter for feature foraging ($M = 3.24$, $SD = 3.19$) than conjunction foraging ($M = 10.64$, $SD = 7.01$), $t(55) = 8.03$, $p < .001$ (PREFER DIFFERENT STATS HERE? CI [-9.25,-5.55]) suggesting more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions. However, both showed significant individual variation: Feature run length varied between 1.87 and 20, and conjunction run length varied between 1.00 and 19.67. Figure 4 (?) depicts run length across the trials separately for each individual. Twenty “super-searchers” were revealed, identified by short run lengths for both feature and conjunction targets [THAT NUMBER IS JUST BASED ON EYE-BALLING THE FIGURE, BUT WE COULD COME UP WITH SOME SORT OF PRECIOUS CUT OFF – WHAT DO YOU THINK?].

@@

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy. As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals’ abilities, such as their information-processing speed and their ability to ignore distractors). Are individuals who are fast on one visual search task fast on another? In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

% Memory stuff might be too left field for intro?
% agree, let's try and mention it in the discussion though. 
In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.

>>>>

In the current study, we focus on one source of individual differences in visual search: strategy. By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation. Perhaps surprisingly, previous literature has shown that both ideal oberver \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise. These apparent contradictory results could potentially expained by large individual differences. Search strategy can also vary in how systematic is it. For example it is common to see top-to-bottom and left-to-right scanning behaviour in scanpaths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.

\end{fmtext}
\maketitle

A striking example of the effect of strategy is given by \cite{boot2006}. They asked participants to monitor a cluttered display for an object changing colour or object onset. Large individual differences were found with respect to the number of saccades participants made while monitoring the stimulus, and this was negatively correlated with detection performance.

In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters. The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} examined strategies in the use of feature-based attention\cite{irons-leber2016,irons-leber2018} \ldots. Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to nearly optimal), and how often they changed search features. Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies. We found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times. Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.

@@

\cite{proulx2011} demonstrated that the different weighting between top-down and bottom-up factors in a conjunction search task explained \ldots Interestingly, they could that around a third of participants were unaware of the search strategy they employed.

A common theme emerging from the studies in the observation that individual strategies vary in their degree of effectiveness or optimality. However, ``visual search'' encompasses a wide range of specific tasks, each tapping into a different aspect of behaviour (feature-based attention, [spatial/fixation patterns??]). The aim of the present study is to investigate the extent to which individual differences are stable across different visual search paradigms. Are observers who use the optimal strategy in the split-half search arrays also more optimal in the ACVS task? Does it make sense to talk about `super-searchers' who show above average performance in a range of search tasks? Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms? As a secondary question, we will measure the test-retest reliability of the differences found in the split-half array paradigm.

@@

The multiple-target foraging results were also in line previous findings \cite{kristjansson2014,johannesson2016}. As expected, run lengths were shorter for feature foraging ($M = 3.24$, $SD = 3.19$) than conjunction foraging ($M = 10.64$, $SD = 7.01$), $t(55) = 8.03$, $p < .001$ (PREFER DIFFERENT STATS HERE? CI [-9.25,-5.55]) suggesting more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions. However, both showed significant individual variation: Feature run length varied between 1.87 and 20, and conjunction run length varied between 1.00 and 19.67. Figure 4 (?) depicts run length across the trials separately for each individual. Twenty ``super-searchers'' were revealed, identified by short run lengths for both feature and conjunction targets [THAT NUMBER IS JUST BASED ON EYE-BALLING THE FIGURE, BUT WE COULD COME UP WITH SOME SORT OF PRECIOUS CUT OFF – WHAT DO YOU THINK?].

@@

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy. As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals' abilities, such as their information-processing speed and their ability to ignore distractors). Are individuals who are fast on one visual search task fast on another? In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

Mention \cite{vogel2008}.
From \cite{proulx2011} - \textit{Vogel and colleagues have found that an individual’s ability to remember a greater number of items using working memory is related to a filtering capacity in visual search that suppresses attentional capture by distracting visual information [10,11,12]. Behavioral work in visual search has extended this research to
demonstrate that working memory correlates only with top-down
visual search performance where task relevance is crucial, but not
with  bottom-up  visual  search  tasks  where  salience  in  the
environment guides attention \cite{sobel2007}}
